---
title: "The variability of sizes in zooplankton species"
categories:
  - Data Sciences I
description: |
  
author:
  - name: Tessa Duhayon
    url: {}
date: 11-17-2020
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
SciViews::R
knitr::opts_chunk$set(echo = FALSE)
```

```{r importation}
data <- read("zooplankton", package = "data.io")
```
**Introduction**

The chosen dataset resumes  1262 observations of 20 variables which are : the equivalent circular diameter, area, perimeter, feret diameter, ellipsoid major axis, ellipsoid minor axis, mean O.D., most frequent O.D., minimal O.D., maximal O.D., O.D. standard deviation, O.D. range, size, aspect ratio, elongation, compactness, transparency, circularity, integrated O.D. and eventually  the class.

# Graphique
```{r}
chart(zooplankton, size ~ class) +
  geom_point() +
  coord_flip()
```
**Interpretation**

We can see that the "Cnidarian" class has the biggest individuals. Their size is well distributed on the graph. The "Protist" class has the smallest individuals. Their size don't exceed 0.3 mm approximately.

Distill is a publication format for scientific and technical writing, native to the web.

Learn more about using Distill at <https://rstudio.github.io/distill>.

